Data Flow Analysis\\in the Presence of Correlated Calls

### 2014-12-05 content/background.tex
started to move proofs to appendix; removing dependency on minted
adding comments
updated reference to Frank's paper

The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs was introduced by F.\,Tip~\cite{frank2014correlated}. The possibility of using IDE to achieve this is mentioned, but not elaborated upon. Our work presents a concrete solution to the problem and an implementation of that solution.

@@

\begin{example}
  Consider the program in Listing~\ref{list:examplejava}. The supergraph corresponding to that program is shown in Figure~\ref{fig:examplesupergraph}.
  \begin{listing}
  \inputMinted{java}{examplesupergraph.java}
  \caption{An example Java program}
  \label{list:examplejava}  
  \end{listing}

@@

\begin{example}\label{ex:constprop}
  One version of the constant propagation analysis that can be encoded with IDE is \textit{linear constant propagation}. A linear constant propagation analysis can detect constants of the form $a\cdot x+b$, where $a$ and $b$ are integers and $x$ is a variable. In particular, a variable can only be considered constant if it depends on at most one other constant variable: even if $y$ and $z$ are variables that are considered constant, the variable $x=y+z$ will be considered not constant. If we encoded the analysis in a way to handle non-linear constant assignments, we would have to use non-distributive flow functions, which would violate the requirements of the IDE algorithm.

@@

  Consider the following program:
\inputMinted{java}{constprop.java}
  For the edges $e_1,\,e_2,\,e_3$, and $e_4$ that start at the first, second, third, and fourth instruction, $M$ creates the following environment transformers:
  \begin{align*}
    M(e_1)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt u\to 1]\\
    M(e_2)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt v\to\textsf{env}(\texttt u)+2]\\
    M(e_3)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt w\to\top]\\
    M(e_4)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt u\to 5].
  \end{align*}

@@

  The result of the analysis yields a map from nodes to environments. Each environment maps variables to elements of the constant-propagation lattice. The environment at the last node will look as follows:
  \[
    \{(\texttt u,\,5),\ (\texttt v,\,3),\ (\texttt w,\,\top)\}.
  \]
\end{example}
\begin{figure}
  \centering
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt,sm]
    \tikzstyle{sm}=[font=\footnotesize]
\begin{tikzpicture}[>=stealth,on grid, auto]
    \node [n,label=$\Lambda$] (zero){};
    \node [n] (zero_) [below=\edge of zero] {};
    \node [n,label={\texttt u}] (u) [right=\dist of zero] {};
    \node [n] (u_) [below=\edge of u] {};
    \node [n,label={\texttt v}] (v) [right=\dist of u] {};
    \node [n] (v_) [below=\edge of v] {};
    \node [n,label=\texttt{w}] (w) [right=\dist of v] {};
    \node [n] (w_) [below=\edge of w] {};
    \node [n] (zero__) [below=\edge of zero_]{};
    \node [n] (u__) [below=\edge of u_]{};
    \node [n] (v__) [below=\edge of v_]{};
    \node [n] (w__) [below=\edge of w_]{};
    \node [n] (zero___) [below=\edge of zero__]{};
    \node [n] (u___) [below=\edge of u__]{};
    \node [n] (v___) [below=\edge of v__)]{};
    \node [n] (w___) [below=\edge of w__]{};  
    \node [n] (zero____) [below=\edge of zero___]{};
    \node [n] (u____) [below=\edge of u___]{};
    \node [n] (v____) [below=\edge of v___)]{};
    \node [n] (w____) [below=\edge of w___]{};

@@

    \path[->] (zero___) edge node[left,sm]{$\id$} (zero____);
    \path[->] (u___) edge node[left,sm]{$\lambda l.5$} (u____);
    \path[->] (v___) edge node[left,sm]{$\id$} (v____);
    \path[->,dashed,color=gray] (w___) edge node[left,sm]{$\id$} (w____);
  \end{tikzpicture}
  \caption[A labeled exploded supergraph for a constant-propagation analysis described in Example~\ref{ex:constprop}]{A labeled exploded supergraph for a constant-propagation analysis described in Example~\ref{ex:constprop}. The dashed edges are edges not reachable from the entry node.}%
  \label{fig:constprop}%
  \end{figure}

>>>>

The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs was introduced by F.\,Tip~\cite{DBLP:journals/scp/Tip15}. The possibility of using IDE to achieve this is mentioned, but not elaborated upon. Our work presents a concrete solution to the problem and an implementation of that solution.

@@

\begin{example}
  Consider the program in Listing~\ref{list:examplejava}. The supergraph corresponding to that program is shown in Figure~\ref{fig:examplesupergraph}.
\begin{figure}
  \centering
  \begin{minipage}{\textwidth}
    \inputMinted{java}{examplesupergraph.java}
  \end{minipage}
  \caption{An example Java program}
  \label{list:examplejava}
\end{figure}

@@

\begin{mdelete}
\begin{example}\label{ex:constprop}
  One version of the constant propagation analysis that can be encoded with IDE is \textit{linear constant propagation}. A linear constant propagation analysis can detect constants of the form $a\cdot x+b$, where $a$ and $b$ are integers and $x$ is a variable. In particular, a variable can only be considered constant if it depends on at most one other constant variable: even if $y$ and $z$ are variables that are considered constant, the variable $x=y+z$ will be considered not constant. If we encoded the analysis in a way to handle non-linear constant assignments, we would have to use non-distributive flow functions, which would violate the requirements of the IDE algorithm.

@@

  Consider the following program:

\inputMinted{java}{constprop.java}
  For the edges $e_1,\,e_2,\,e_3$, and $e_4$ that start at the first, second, third, and fourth instruction, $M$ creates the following environment transformers:
  \begin{align*}
    M(e_1)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt u\to 1]\\
    M(e_2)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt v\to\textsf{env}(\texttt u)+2]\\
    M(e_3)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt w\to\top]\\
    M(e_4)
    &=\lambda\textsf{env}\,.\,\textsf{env}[\texttt u\to 5].
  \end{align*}

@@

  The result of the analysis yields a map from nodes to environments. Each environment maps variables to elements of the constant-propagation lattice. The environment at the last node will look as follows:
  \[
    \{(\texttt u,\,5),\ (\texttt v,\,3),\ (\texttt w,\,\top)\}.
  \]
\end{example}

\begin{figure}
  \centering
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt,sm]
    \tikzstyle{sm}=[font=\footnotesize]
\begin{tikzpicture}[>=stealth,on grid, auto]
    \node [n,label=$\Lambda$] (zero){};
    \node [n] (zero_) [below=\edge of zero] {};
    \node [n,label={\texttt u}] (u) [right=\dist of zero] {};
    \node [n] (u_) [below=\edge of u] {};
    \node [n,label={\texttt v}] (v) [right=\dist of u] {};
    \node [n] (v_) [below=\edge of v] {};
    \node [n,label=\texttt{w}] (w) [right=\dist of v] {};
    \node [n] (w_) [below=\edge of w] {};
    \node [n] (zero__) [below=\edge of zero_]{};
    \node [n] (u__) [below=\edge of u_]{};
    \node [n] (v__) [below=\edge of v_]{};
    \node [n] (w__) [below=\edge of w_]{};
    \node [n] (zero___) [below=\edge of zero__]{};
    \node [n] (u___) [below=\edge of u__]{};
    \node [n] (v___) [below=\edge of v__)]{};
    \node [n] (w___) [below=\edge of w__]{};  
    \node [n] (zero____) [below=\edge of zero___]{};
    \node [n] (u____) [below=\edge of u___]{};
    \node [n] (v____) [below=\edge of v___)]{};
    \node [n] (w____) [below=\edge of w___]{};

@@

    \path[->] (zero___) edge node[left,sm]{$\id$} (zero____);
    \path[->] (u___) edge node[left,sm]{$\lambda l.5$} (u____);
    \path[->] (v___) edge node[left,sm]{$\id$} (v____);
    \path[->,dashed,color=gray] (w___) edge node[left,sm]{$\id$} (w____);
  \end{tikzpicture}
  \caption[A labeled exploded supergraph for a constant-propagation analysis described in Example~\ref{ex:constprop}]{A labeled exploded supergraph for a constant-propagation analysis described in Example~\ref{ex:constprop}. The dashed edges are edges not reachable from the entry node.}%
  \label{fig:constprop}%
  \end{figure}
\end{mdelete}

### 2014-12-05 content/eval.tex
updated reference to Frank's paper

Finally, correlated calls can occur on multiple receivers and other scenarios discussed in~\cite{frank2014correlated} that are not handled in this work.

>>>>

Finally, correlated calls can occur on multiple receivers and other scenarios discussed in~\cite{DBLP:journals/scp/Tip15} that are not handled in this work.

### 2014-12-05 content/intro.tex
adding comments
updated reference to Frank's paper

We improve the precision of IFDS problem solutions by eliminating infeasible paths that occur in object-oriented programs in the presence of \textit{correlated method calls}~--- polymorphic calls that are invoked on the same object~\cite{frank2014correlated}.

@@

The remainder of this paper is organized as follows. In the next section, we describe the IFDS and IDE analyses in detail. In Section~\ref{chapter:cca} we present the correlated-calls analysis as a transformation of IFDS problems into a special kind of IDE problem. Section~\ref{sec:ccdatastr} describes an efficient representation of the data structures that are required to define a correlated-calls IDE transformation.
In Section~\ref{chapter:eval} we address some implementation aspects of the correlated-calls analysis and present an evaluation of its results. Section~\ref{chapter:concl} contains concluding remarks.

>>>>

We improve the precision of IFDS problem solutions by eliminating infeasible paths that occur in object-oriented programs in the presence of \textit{correlated method calls}~--- polymorphic calls that are invoked on the same object~\cite{DBLP:journals/scp/Tip15}.

@@

\mtodo{Reference appendix?}The remainder of this paper is organized as follows. In the next section, we describe the IFDS and IDE analyses in detail. In Section~\ref{chapter:cca} we present the correlated-calls analysis as a transformation of IFDS problems into a special kind of IDE problem. Section~\ref{sec:ccdatastr} describes an efficient representation of the data structures that are required to define a correlated-calls IDE transformation.
In Section~\ref{chapter:eval} we address some implementation aspects of the correlated-calls analysis and present an evaluation of its results. Section~\ref{chapter:concl} contains concluding remarks.
